What can we learn about life in the city by mining the Melbourne’s Open Data Platform?

### 2017-05-03 thesis/proposal_draft.Rmd
update night 3

@@

## References  
  1. City of Melbourne, _'About Melbourne Data'_, https://data.melbourne.vic.gov.au/about,  
  _accessed 18 April 2017_  
  2. City of Melbourne, _'Pedestrian Counting System'_,  
  http://www.pedestrian.melbourne.vic.gov.au/pdf/CityofMelbournePedestrianCountingSystem.pdf 
  4 May 2015, _accessed 18 April 2017_  
  3. Christopher G. Healey, _'Attention and Visual Memory in Visualization and Computer Graphics'_, IEEE Transactions on Visualization and Computer Graphics,  
  https://www.csc2.ncsu.edu/faculty/healey/download/tvcg.12a.pdf

>>>>

The use of weather data to improve forecasting performance would be ideal, due to the availability of weather forecasts compared to many other forms of data. Machine learning techniques will also be explored. In particular, clustering of sensor locations may be useful in identifying patterns at certain types of location, such as tourist attractions and shopping districts.

@@

Once a model for forecasting the data has been established, an interactive web application to present the model will be developed. A key aspect which we want to include is the ability for the end user to forecast pedestrian activity in the future.

## References  
  1. City of Melbourne, _'About Melbourne Data'_, https://data.melbourne.vic.gov.au/about,  
  _accessed 18 April 2017_  
  2. City of Melbourne, _'Pedestrian Counting System'_,  
  http://www.pedestrian.melbourne.vic.gov.au/pdf/CityofMelbournePedestrianCountingSystem.pdf 
  4 May 2015, _accessed 18 April 2017_  
  3. Healey, Christopher G.,  _'Attention and Visual Memory in Visualization and Computer Graphics'_, IEEE Transactions on Visualization and Computer Graphics,  
  https://www.csc2.ncsu.edu/faculty/healey/download/tvcg.12a.pdf
